### 2013-03-14 doc/sosp13/abstract.tex
minor mods to abstract, intro, 1st paragraph of relatedwork; added missing citations to bib. 	modified:   abstract.tex 	modified:   intro.tex 	modified:   paper.bib 	modified:   relatedwork.tex

Grappa is a runtime system for commodity clusters of multicore computers that
exposes a massively parallel and single address space abstraction to
applications. Grappa's goal is to provide scalable performance for irregular
parallel applications, such as graph processing. These applications are
challenging because they exhibit little data locality, unbalanced parallel
work and complex communication patterns.

>>>>

Grappa is a runtime system for commodity clusters of multicore computers that
presents a massively parallel, single address space abstraction to
applications. Grappa's goal is to provide scalable performance for irregular
parallel applications, such as graph processing. These applications are
challenging because they exhibit little data locality, imbalanced parallel
work and complex communication patterns.
